### 2009-12-08 docs/marcello-dissertation/thesis/preamble.tex
First Draft of the dissertation peer reviewed with Kleber.
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@680 559edde2-a4d4-44e0-96fc-4035e40d7396

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Sensor Networks are becoming more and more important to different science
communities bacause of what it produces: the raw data for different studies.
In order to make use the collected data, researchers may have to dissect the
characteristics of the sensor network in question, regarding different
properties such as the purpose and location of the observed data, as well as
how the data is described. In this way, this work first proposes a set of
taxonomies that can be used to study and classify a given instance of sensor
network and its produced data. Then, based on the classes of these taxonomies, 
this work selected a Document-Oriented Database system as a result of an
empirical evaluation of the requirements for a new persistence layer for 
NetBEAMS, the case study used in this work. For this reason, the design and
implementation of a new data persistence component for NetBEAMS show how
schema-less data models help decreasing the complexity related to the database
layer, not yet reported by the state of the art. Furthermore, this work also
proposes the use of Database Shards in order support the implementation of
Data-Centric sensor networks. 
}
\vspace*{\fill}

>>>>

%\doublespacing{\noindent
\onehalfspacing{\noindent      
Sensor Networks are becoming more and more important to different science
communities bacause of what they produce: the raw data for different studies.
In order to make use the collected data, researchers may have to dissect the
characteristics of the sensor network in question, regarding different
properties such as the purpose and location of the observed data, as well as
how the data is described. For this reason, this work proposes a set of data
persistence taxonomies based on the state of the art, which can be used to
classify the properties of the produced raw data. In order to evaluate the
proposed taxonomies, this work designs and implements a data persistence
component for NetBEAMS, our case study of modular sensor network infrastructure
developed to improve the operation of the SF-BEAMS environmental sensor
network. In this way, based on empirical analysis regarding proposed
taxonomies for the case study, this work selected mongoDB, a schema-less
document-oriented database instead of the traditional use of relational
databases. As a result based on the experiments conducted, this work suggests
that use of Key-Value Pair datasents in orde tor provide External of
Data-Centric approach. Therefore, the use of a solution of the help decreasing
the complexity related to the data persistence layer for sensor networks with
external or data-centric storage mechanism, and whose purpose is data
archival. Finally, this work proposes different future works such a
data-centric approach using Databa se Shards to store te collected data and Map
Reduce to execute parallel queries over the shards.} \vspace*{\fill}
